---
title: "Gibbs Sampler"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GibbsSampler}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(GibbsSamplerHW)
```


# My Function

I created a function called rbvnorm() that goes through the Gibbs Sampling Process to produce a sample from the bivariate normal. It relies on the number of desired iterations/samples and the distribution of the bivariate normal (mean and covariance matrix). You can see my function below.

```{r}
rbvnorm <- function(iter, mu, sigma){
  x2 <- mu[2]
  df <- matrix(data=NA, nrow=iter,ncol=2)
  colnames(df) <- c("x1", "x2")
  for (i in 1:iter){
    x1 <- rnorm(1, mu[1] + (sigma[1,2]/sigma[2,2])*(x2 - mu[2]), sigma[1,1]-sigma[1,2]*(1/sigma[2,2])*sigma[2,1])
    df[i,1] <- x1
    x2 <- rnorm(1, mu[2] + (sigma[2,1]/sigma[1,1])*(x1 - mu[1]), sigma[2,2]-sigma[2,1]*(1/sigma[1,1])*sigma[1,2])
    df[i,2] <- x2
  }
  invisible(list(gibbs = df, iter = iter, mu = mu, sigma = sigma))
}
```


# Testing My Function

You can see my function in action below. I have saved the output in an object called "output" and displayed each of the parts of it below, including the first few samples, the number of iterations, the mean, and the covariance matrix.

```{r}
output <- rbvnorm(iter = 10000, mu = c(3,6), sigma = matrix(c(8,-2,-2,4), nrow =2, byrow = TRUE))
output$iter
output$mu
output$sigma
tail(output$gibbs)
```

